Covid-19 análise espaço-temporal.

### 2020-11-02 Notebooks/intr_results.rmd
Update intr_results.rmd

 Já o Índice de Moran local (*LISA*) é calculado pela seguinte equação:
 $$I(i) = \frac{x_{i}-\overline x}{s^{2}}\sum_{j=1}^{n}w_{ij}(x_{j}-\overline{x})$$

>>>>

 Já o Índice de Moran local (*LISA*) é calculado pela seguinte equação:
 $$I(i) = \frac{x_{i}-\overline x}{s^{2}}\sum_{j=1}^{n}w_{ij}(x_{j}-\overline{x}), i=1,...,n$$
